The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field

### 2013-07-30 writedown/npt-neq/alanine.tex
backup manuscript

\newpage

@@

The aformentioned nonequilibrium molecular dynamicses simulation algorithm
does not describe how the boundary of the system should be set up. The 100\% save
method is to simulate a infinitely large isolated system, or any large enough
isolated subsystem of it. In practice, it is both impossible and unnecessary to
do such a simulation. In practice, proper boundary condition should be developped
based on how the nonequilibrium system is set up, and what are the nonequilibrium
observables to measure.
Since we are mainly interested in the non-thermal effect of
the electric field to the configuration of a solvated alanine dipeptide,
we assume the alanine is embeded into an infinitely large solvent envrionment,
and the electric field is only applied to the neighborhood of the alanine. Therefore, 
extra heat generated by turing on the electric field can be effectively absorbed
by the envrionment.

@@

\section{Example I: Alanine dipeptide
  under a linearly switching on electric field}

\subsection{System setting up }
\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[]{fig.ala/fig-field-dipol.eps}
  \caption{The magnitude of the external electric field, and the
    x-component of the dipole moment of the alanine molecule as a
    function of time. The dashed lines are the strengths of the
    external electric field, while the solid lines are the dipole
    moments. Three test cases are indicated by different colors.}
  \label{fig:tmp3}
\end{figure}

We want to study the nonequilibrium properties of an alanine dipeptide
under a changing electric field. As a model system, we study the
linearly switching on electric field: From $t=0$ to
$t=t_{\textrm{init}}$, the strength of the field grows linearly, while
after $t=t_{\textrm{init}}$, the strength is kept constant at
$E_{\textrm{max}}$. Fig.~\ref{fig:tmp3} shows the three different
cases considered in this work: $t_{\textrm{init}} = 10$, 100, and
500~ps, and 
in all cases the maximum strength of the electric field is
$E_{\textrm{max}} = 1$~V/nm.
The direction of this field is arbitarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction (see also Fig.~\ref{fig:tmp3} for
the vanished initial dipole moment), applying the electric along x-axis is
not biased.
The size of the system is $2.67\times 2.67\times
2.67\, \textsf{nm}^3$, with one alanine dipeptide described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{nm} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
5~\textsf{ps}.  They server as starting point of the branching
trajectories. The branching trajectories were integrated by the
Leap-frog scheme with the aformentioned nonequilibrium temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dyanmics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, it does not have an obviously effect on the
dyanmics of the system.

@@

On each branching trajectory, to easy the analysis, the conformation
of the alanine dipeptide is plotted by the Ramachandran histogram, as
shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
conformation is given in the left plot, and the fully relaxed
conformation at $E_{\max} = 1$~V/nm is given in the right plot.  It is
clear the conformations are populated in several clusters, and the
position of the clusters do not change when the external electric
field is applied. This means that only a few of the configurations are likely to be observed, while there is nearly
no oppotunity to see others. 
These configurations are called ``metastable states''. The strict definition of the
metastability is not exactly the same as those conformations that are likely to be observed.
Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
we assume they have the same meaning.
We manually divide the
$\psi$--$\phi$ plane into 5 subregions, see Fig.~\ref{fig:tmp4},
then the observation on the Ramachandran histogram is projected to the
observation of these 5 subregions.  These subregions
correspond to different secondary structure of a peptide chain:
$A_1$ and $A_2$ are
corresponding to the alpha helix. $B_1$ and $B_2$ are
corresponding to beta sheet. $C$ is corresponding to the
left-handed alpha helix.

@@

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
metastable sets changes due to the external electric field, for
example, the population of conformations C vanishes in equilibrium,
but plays an important role when the electric field is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast is the change, and the relation to the speed of
the increasing electric field (i.e. the value of $t_{init}$). 
Firly, we study the population of the metastable conformations
Being more strict, we calculate the nonequilibrium observable
\begin{align}
  p_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\}
\end{align}
Secondly, we study the
forward and backward transition probability of the metastable conformations, which is defined by
\begin{align}
  p^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
  p^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I)
  \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
where $\Delta t$ is the time-scale of the observation.
For a revserible and homogeneous Markov process, it is easy to show
that $p^{\fwd}_{J,I} = p^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
process considered by the present work, this relation is genarlly not guarenteed.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
  \label{fig:tmp6}
\end{figure}

For all testing cases, the maximum strength of the electric field
$E_{\textrm{max}}$ is chosen to be 1~\textsf{V/nm}.  Three values of
$t_{\textrm{init}}$ (10~\textsf{ps}, 100~\textsf{ps} and
500~\textsf{ps}) are chosen to study the response of the system to the
external electric field perturbation. The result is given in
Fig.~\ref{fig:tmp5}.  No matter how fast is the electric field turned
on, the beta sheet configuration, which presents at the beginning,
fades away as the system relaxes to the new equilibrium. The
population of alpha helix $A_1$ configuration grows from 45\% to 70\%.
alpha helix $A_2$  does not change a lot under the electric field.
The ill-folding configuration $C$ noticeably grows from 0\% to 20\%.
\\

In the case of fastly switching on electric field
($t_{\textrm{init}}=10~\textsf{ps}$), the dynamics of the population
of the metastable sets shows three different time-scales. (1) From
$t=0$ to 10~\textsf{ps}, the population of $A_2$ fastly increases,
while the population of $A_1$ decreases with the same amount, so it is
reasonable to argue that there is a fast configurational change from
$A_1$ to $A_2$. Please see, in Fig.~\ref{fig:tmp5}, the green and read
peak around $t = 10~\textsf{ps}$. At the same time, the population of
other metastable sets remains unchanged.  (2), From $t=10$ to
40~\textsf{ps}, the population of $B_2$ decreases by 0.15, and this
configuration almost disappears. Interestingly, the population of $A_1$
increases by the same amount, and the population of $A_2$ goes back to
the initial value. The populations of $B_1$ and $C$ start increasing
and decreasing, correspondingly. The speed of these changes are much
slower than that of $B_2$ and $A_1$.  (3) At the time scale of $t =
300~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
the non-equilibrium steady state (system with $E(\infty) = 1~\textsf{V/m}$).
This time is actually thirty times large than when the electric field
is fully switched on ($t_{\textrm{init}} = 10~\textsf{ps}$). This 
indicates that the internal time scale of $A_1$, $B_1$ and $C$
relaxation is around $300~\textsf{ps}$.\\

To further test the dynamics of metastable population, two simulations
of $t_{\textrm{init}} = 100~\textsf{ps}$ and $t_{\textrm{init}} =
500~\textsf{ps}$ are performed. The first time scale of $t =
10~\textsf{ps}$ disappears in both of the testing simulations. In the
simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
$A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
around $300~\textsf{ps}$. This further verifies internal time scale of
$A_1$, $B_1$ and $C$ presented in the testing case of
$t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
faster: it decays to zero as fast as the external electric field is
switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
growth of the external electric field is slower than the longest
internal time scale of system, which means that the changes of the
perturbation to the system is so slow that the system can catch up
with that. The numerical results show the same story: the relaxation
of all populations are around $500 \sim 600~\textsf{ps}$.
\\

@@

\section{Testing the effect of the thermostat and barostat}

% \section{System set up}

% $R_{\textrm{ex}}$ was chosen to be
% $1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
% 0.1~\textsf{ps}$) was applied to water molecules that were more than
% $1.0$~\textsf{nm} away from the center of the simulation box. In
% addition, a Parrinello-Rahman barostat was couple to the system with a
% time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$.

>>>>

\section{Introduction}

The possible effect of the electric field (EF) on the conformation of
proteins gains increasing attantion recently, because it closly
related to the health problem of exposing human tissue in the
electromagnetic radiation. Despite the importance of this problem, a
complete understanding of how the electric field influnece the  protein
is still lacking, therefore, a conserderable number of
experimental~\cite{bohr2000microwave, bohr2000microwave-1,
  dePomerai2000cell, inskip2001cellular, mancinelli2004non} and
theoretical~\cite{budi2005electric, budi2007effect,
  budi2008comparative, toschi2008effects, astrakas2011electric,
  astrakas2012structural, damm2012can, starzyk2013proteins,
  english2009nonequilibrium, solomentsev2012effects} studies have been devoted to this topic,
and the references listed above is far from complete.

The molecular dynamics (MD) simulation has been proved to be useful in
understanding the behavior of a protein (or a short peptide segment)
in both static and oscilatatory electiric
fields~\cite{budi2005electric, budi2007effect, budi2008comparative,
  toschi2008effects, astrakas2011electric, astrakas2012structural,
  damm2012can, starzyk2013proteins, english2009nonequilibrium,
  solomentsev2012effects}. In these studies, the initial
configurations are usually taken from the Protein Data Bank (PDB).
And then the temperature controlled simulation are performed for from
a few to tens of nanoseconds, during which the interested
conformational chanages can be observed. Along the trajectories, the
secondary structure, root mean square displacement (RMSD), the dipole
moment and some shape parameters are calculated and investigated by
either plotted as a function of time, or doing time average over the
whole simulation. This approach release useful information on how the
secondary structure is changed by external electiric field.  However,
by plotting the quantities against time, one may observe strong
fluctuation in plots, which hintered the quantitative and conclusive
analysis on what is happening during the conformational change, when
it happens and what is the strength. Although the statistical
uncertainty in the time-averaged observations are small, the
time-average itself is not well defined for a nonequilibrium process
such as relaxing process to the new conformations under static
electiric field, and the dynamics under oscilatating electric field.

The dynamical nonequilibrium molecular dyanmics simulation (D-NEMD)
was firstly developed by G. Ciccotti and his
colleagues~\cite{ciccotti1975direct, ciccotti1979thought}, and
recently successfully applied to the study of
hydrodynamics~\cite{orlandini2011hydrodynamics,
  orlandini2011hydrodynamics-01}. D-NEMD provides a way of evaluating
nonequilibrium observables by doing an ensemble of nonequilibrium MD
simualtions.  This provides a promising way of analysing the
conformational changing under a generally time-dependent electric
field. In the present paper, we study the minimal model peptide
segment -- alanine dipeptide. We take the approach of starting from a
single peptide rather than a more realistic chain, firstly because it
is easier to draw clear conclusions on the nonequilibrium properties
of a single peptide by excluding all possible interplay between
different peptide segments along a chain, then construct the chain
nonequilibrium properties from the well-studied single peptides.
Secondly, the current computationl resource available is not enought
to study peptide chains by D-NEMD, since one needs to simualte an
ensemble of MD trajectories (typically a few thousands), so it
requires much higher computational cost than producing a single MD
trajectory.

In this paper, we firstly describe the idea of the D-NEMD, then
observables helping us the analyze the nonequilibrium properties
(i.e., the dipole moment, time-dependent properties of being a certain
conformation, the nonequilibrium transition properties and the net
property flux) are introduced. The numerical results of alanine
dipeptide under static and sine-shaped oscilatating electric field are
presented. By calculating the nonequilibrium properties from the D-NEMD
simulations, we are able to answer from which to which the conformation
changes, when do these changes happend, and how strong are the changes.
As far as we know, our simulation is the first D-NEMD simulation
on the electric field effect on alanine dipeptide, and provides new
information helping people better understand the nonequilibrium
effect of electric field on the protein conformation.

@@

The aformentioned nonequilibrium molecular dynamicses simulation algorithm
does not describe how the boundary of the system should be set up. The 100\% save
method is to simulate a infinitely large isolated system, or any large enough
isolated subsystem of it. In practice, it is both impossible and unnecessary to
do such a simulation. In practice, proper boundary condition should be developped
based on how the nonequilibrium system is set up, and what are the nonequilibrium
observables to measure.
Since we are mainly interested in the nonthermal~\cite{delaHoz2005microwaves} effect of
the electric field to the configuration of a solvated alanine dipeptide,
we assume the alanine is embeded into an infinitely large solvent envrionment,
and the electric field is only applied to the neighborhood of the alanine.
Therefore, 
extra heat generated by turing on the electric field can be effectively absorbed
by the envrionment.
It is argued that 
an accurate reaction temperature control is essential for being able to perform
reproducible experiments~\cite{damm2012can}.

@@

\section{Example I: Alanine dipeptide
  under a constant electric field}

\subsection{System settings and simulation protocol}
\begin{figure}
  \centering
  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \includegraphics[]{fig.ala/fig-field-dipol.eps}
  \caption{The magnitude of the external electric field, and the
    x-component of the dipole moment of the alanine molecule as a
    function of time. The dashed lines are the strengths of the
    external electric field, while the solid lines are the dipole
    moments. Three test cases are indicated by different colors.}
  \label{fig:tmp3}
\end{figure}

We want to study the nonequilibrium properties of an alanine dipeptide
under a changing electric field. As a model system, we study the
a constant electric field. At time $t=0$~ps, the system
has been fully equilibriated without any electric field. From $t=0$ to
$t=t_{\textrm{init}}$, the electic field is switched on linearly, while
after $t=t_{\textrm{init}}$, the field is kept constant at
$E_{\infty}$. Fig.~\ref{fig:tmp3} shows the three different
cases considered in this work: $t_{\textrm{init}} = 10$, 100, and
500~ps, and 
in all cases the maximum strength of the electric field is
$E_{\infty} = 1$~V/nm.
The direction of this field is arbitarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction (see also Fig.~\ref{fig:tmp3} for
the vanished initial dipole moment), applying the electric along x-axis is
not biased.
The size of the system is $2.67\times 2.67\times
2.67\, \textsf{nm}^3$, with one alanine dipeptide described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{nm} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
5~\textsf{ps}.  They server as starting point of the branching
trajectories. The branching trajectories were integrated by the
Leap-frog scheme with the aformentioned nonequilibrium temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dyanmics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, it does not have an obviously effect on the
dyanmics of the system.

@@

On each branching trajectory, to easy the analysis, the conformation
of the alanine dipeptide is plotted by the Ramachandran histogram, as
shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
conformation is given in the left plot, and the fully relaxed
conformation at $E_{\infty} = 1$~V/nm is given in the right plot.  It is
clear the conformations are populated in several clusters, and the
position of the clusters do not change when the external electric
field is applied. This means that only a few of the configurations are likely to be observed, while there is nearly
no oppotunity to see others. 
These configurations are called ``metastable states''. The strict definition of the
metastability is not exactly the same as those conformations that are likely to be observed.
Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
we assume they have the same meaning.
We manually divide the
$\psi$--$\phi$ plane into 5 subregions, see Fig.~\ref{fig:tmp4},
then the observation on the Ramachandran histogram is projected to the
observation of these 5 subregions.  These subregions
correspond to different secondary structure of a peptide chain:
$A_1$ and $A_2$ are
corresponding to the alpha helix. $B_1$ and $B_2$ are
corresponding to beta sheet. $C$ is corresponding to the
left-handed alpha helix.

@@

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
metastable sets changes due to the external electric field, for
example, the population of conformations C vanishes in equilibrium,
but plays an important role when the electric field is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast is the change, and the relation to the speed of
the increasing electric field (i.e. the value of $t_{init}$). 
Firly, we study the population of the metastable conformations
Being more strict, we calculate the nonequilibrium observable
\begin{align}
  p_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
which is the time dependent probability of the alanine being in metastable
state $I$.
Secondly, we study the
forward and backward transition probability of the metastable conformations, which is defined by
\begin{align}
  P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
  P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
  % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
where $\Delta t$ is the time-scale of the observation.
For a revserible and homogeneous Markov process, it is easy to show
that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
process considered by the present work, this relation is genarlly not guarenteed. Finally, we study the backward net flux from metastable set $I$ to $J$:
\begin{align}
  F^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J).
\end{align}
Unlike the transition probabilities that are defined by the conditional
probability, the net flux is defined by the difference between
two joint probabilities, and prensents how much conformation $J$ is changed
into $I$ in the past $\Delta t$ interval. A positive value indicates the
flux from $J$ to $I$, while a negative value indicates a flux from $I$ to $J$.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}
  \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
  \label{fig:tmp6}
\end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-5.eps}\\
%   % \caption{The populations of the metastable sets as a function of time.
%   %   The dashed vertical lines indicate the three different time scale of
%   % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-5.eps}\\
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-5.eps}
%   \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
%   \label{fig:tmp6}
% \end{figure}

The time-dependent probability of the system in a certain metastable set is given in
Fig.~\ref{fig:tmp5}, and different speeds of switching on the electric field
($t_{init} = 10$, 100 and 500~ps) are compared.  No matter how fast is the electric field turned
on, the beta sheet configuration, which presents at the beginning,
fades away as the system relaxes to the new equilibrium. The
population of alpha helix $A_1$ configuration grows from 45\% to 70\%.
alpha helix $A_2$  does not change a lot under the electric field.
The left-hand helix configuration $C$ noticeably grows from 0\% to 20\%.

For the case of fastly switching on electric field
($t_{\textrm{init}}=10~\textsf{ps}$),
we plot the time-dependent forward, backward transition probability and the net backward probability flux
in Fig.~\ref{fig:tmp6}.
If the process were time reversible and homogeneous, then the forward and backward transition probabilities
would be identical. As a matter of fact, the inconsistent forward and backward transition probabilities
implies the process is indeed nonequilibrium.
Together with Fig.~\ref{fig:tmp5}, we observe
three different timescales of 
the dynamics of the alanine conformation:
(1) From
$t=0$ to approximately 20~\textsf{ps}, the population of $A_1$ firstly decreases and then increases to the original value,
while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
there is firstly a fast probability flux (conformational change) from
$A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
$A_2$ to $A_1$.
In the meanwhile, a clear trend from $\beta$-sheet conformations ($B_1$ and $B_2$)
into $\alpha$-helix conformations ($A_1$, $A_2$ and $C$), both left- and right-handed,
has been established.
Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
The population of $B_1$ remains almost unchanged,
because it  at the same time loses population to $\alpha$-helix conformations.
Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
decrease of $B_2$ population between 10 and 20~ps.
(2), From $t=10$ to
100~\textsf{ps},
The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
gradually decays to 0. Conformational change between $\alpha$-helix and $\beta$ sheet
is hardly observed, except a very week flux from $B_1$ to $A_1$ and $C$, which will be discussed later.
At this stage, the population of $B_2$ decreases to almost 0, while the population of $A_2$
converge to a non-vanishing value of approximately 0.06.
% the population of $B_2$ decreases by 0.15, and this
% configuration almost disappears. Interestingly, the population of $A_1$
% increases by the same amount, and the population of $A_2$ goes back to
% the initial value. The populations of $B_1$ and $C$ start increasing
% and decreasing, correspondingly. The speed of these changes are much
% slower than that of $B_2$ and $A_1$.
(3) At the time scale of $
500~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
the non-equilibrium steady state (system with $E(\infty) = 1~\textsf{V/m}$).
We only observed slowing decaying probability flux from $B_1$ to $A_1$ and $C$.
The maganitude of the flux from $B_1$ to  $C$ is larger than that from  $B_1$ to  $A_1$.
It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
population with $A_2$, and $B_1$ exchange
population with $B_2$. However, when the $C$ conformation hardly changes
to any other conformation, as indicated by the almost 1 value of the forward
transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
acutally more stable than  other conformations.
This time-scale is actually 50 times large than when the electric field
is fully switched on ($t_{\textrm{init}} = 10~\textsf{ps}$).
Notice that the Fig.~\ref{fig:tmp3}
shows that the x-component of the dipole moment of the alanine dipeptide
reaches the maximum value at a time scale  that is the same as
$t_{init}$. This observation indicates that the alanine can adjust almost immediately its
dipole according to the external electric field, however, the conformational change
happens at some much slower time scales.

To further test the dynamics of metastable population, two simulations
of $t_{\textrm{init}} = 100~\textsf{ps}$ and $t_{\textrm{init}} =
500~\textsf{ps}$ are performed. The first time scale of $t =
20~\textsf{ps}$ disappears in both of the testing simulations. In the
simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
$A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
around $500~\textsf{ps}$. This further verifies internal time scale of
$A_1$, $B_1$ and $C$ presented in the testing case of
$t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
faster: it decays to zero as soon as the external electric field is fully
switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
growth of the external electric field is comparable to the longest
internal time scale of system, which means that the changes of the
perturbation to the system is so slow that the system can catch up, so
the process can be treated as  quasi-equilibrium.
The numerical results show the same story: the relaxation
of all populations are around $500 \sim 600~\textsf{ps}$.

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-conv.eps}
  \caption{The populations of the metastable sets as a function of time.
    The dashed vertical lines indicate the three different time scale of
  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  \label{fig:tmp7}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-mode2-010.eps}
  \includegraphics[]{fig.ala/fig-meta-mode2-040.eps}
  \includegraphics[]{fig.ala/fig-meta-mode2-200.eps}
  \caption{The populations of the metastable sets as a function of time.
    The dashed vertical lines indicate the three different time scale of
  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  \label{fig:tmp5}
\end{figure}

@@

% \section{Testing the effect of the thermostat and barostat}

% % \section{System set up}

% % $R_{\textrm{ex}}$ was chosen to be
% % $1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
% % 0.1~\textsf{ps}$) was applied to water molecules that were more than
% % $1.0$~\textsf{nm} away from the center of the simulation box. In
% % addition, a Parrinello-Rahman barostat was couple to the system with a
% % time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$.

% Let's consider an infinitely large NVE system (here we call it
% "universe"). Some interesting process is happening in a small
% subsystem. For equilibrium phenomena, this subsystem is the usually
% considered as NVT (or NPT, $\mu$VT, depends on how the question is
% raised) system.  In simulations, we only simulate the subsystem and
% use the thermostat to mimic the embedment into the universe.  For
% non-equilibrium simulation, we also want to simulate only the
% subsystem of interest, but the physical meaning of directly applying a
% thermostat designed for generating equilibrium ensemble is not clear
% to a non-equilibrium process. Moreover, there is no unique way of
% defining how the subsystem is coupled into the universe: It is subject
% to how the perturbation comes into the subsystem, and how the energy
% of the system dissipates into the universe. In the case of switching on
% electric field system, two limiting scenarios are considered by us: (1)
% The subsystem is isolated from the universe: The electric field is
% applied to a system that conserves the energy, volume and number of
% particle (i.e. a NVE subsystem in short).  The isolation here means
% that the subsystem does not exchange energy, volume and number of
% particle with the universe, but the perturbation (electric field) does
% come in to the subsystem.  The periodic boundary condition is applied
% here only to avoid the difficulty of defining a experimental
% meaningful boundary in simulation.  In this scenario, the size the
% subsystem is somewhat arbitrary (it depends on experimental setting),
% therefore, it is important to consider the convergence of the
% simulation result with respect to the size of the subregion.  (2) The
% system exchange the energy, volume and particle with the universe, and
% the universe is so big that the perturbation in the subsystem will not
% kick the universe from equilibrium.  In practice, it is impossible to
% simulate the infinite large universe, Instead, we want to simulate the
% considerably smaller subsystem instead.  The idea is to divide the
% simulation region into two parts (see Fig.~\ref{fig:tmp2}): the first
% is called \emph{Newtonian dynamics region} that is a region around the
% molecule of interest, where the dynamics is Newtonian. Note that the
% molecular trajectories in the Newtonian dynamics region are the same
% as if it were couple to the universe, only when a proper boundary
% condition is provided. Strictly speaking, the boundary should be
% provided by the out side infinitely large universe, which immediately
% leads back to the numerical difficulty of simulating a infinite large
% system. However, we notice that the detailed information
% (i.e. position and velocity) of the every molecule outside the
% Newtonian dynamics region is not relevant to the non-equilibrium
% behavior of the molecule of interest, because we are only interest in
% the non-equilibrium averages, which does not depends on the individual
% trajectory, but on the trajectorial ensemble sampled by the
% non-equilibrium simulation.  Therefore, the universe, as a boundary to
% the Newtonian dynamics region, can be replace by
% an efficiently thermo- and barostated subsystem, as indicated by the gray
% part of Fig.~\ref{fig:tmp2}. 
% % That is to say the subsystem is coupled to a
% % thermostat, a barostat and a particle bath with infinitely high
% % efficiency. Practically, it is impossible to simulation with a
% % ``infinitely fast'' thermostat, barostat and particle bath.
% We indicate the radius of the Newtonian dynamics region by
% $R_{\textrm{ex}} = 1~\textsf{nm}$ (see Fig.~\ref{fig:tmp2} for
% explanation), and couple it to very sufficient thermo- and
% barostat. We use a Langevin thermostat coupled to the thermostating
% region with a time-scale of $\tau_{T} = 0.1~\textsf{ps}$, and a
% Parrinello-Rahman barostat with a time-scale of $\tau_{P} =
% 2.0~\textsf{ps}$.

% The non-equilibrium steady temperature and pressure of the
% non-thermostated simulation are $330$ K and $-500$ Bar,
% correspondingly. Those of the thermostated system are $300$ K and 1
% Bar, correspondingly. Therefore, we can see from Fig.~\ref{fig:tmp6}
% that the relaxation of the thermostated system is faster than the
% non-thermostated system. The three time-scale of metastable population
% dynamics in the thermostated system is consistent with that of the
% non-thermostated system. This means that thermostating, in this case,
% does not qualitatively change the population dynamics of metastable
% states.
